Project-I by Group MexicoCity

### 2014-11-03 report/paper.tex

\subsection{Penalized logistic regression}
We could improve the test error by cross-validation. The Figure \ref{fig:crossval} shows the three different test error RMSE, 0-1 loss and logloss. We used different numbers of seed to have a better prediction for our test error.
\begin{figure}
\centering
\subfigure[0-1 loss]{\includegraphics[width=0.5\textwidth]{images/penLogRegCrossVall01Loss.eps}}
\subfigure[rmse]{\includegraphics[width=0.5\textwidth]{images/penLogRegrmse.eps}}
\subfigure[log loss]{\includegraphics[width=0.5\textwidth]{images/penLogRegLogloss.eps}}
\caption{Cross-validation : penalized logistic regression with different lambda values}
\label{fig:crossval}
\end{figure} 
\subsection{Feature transformations}

>>>>

\subsection{Penalized logistic regression}
We could improve the test error by cross-validation. The Figure \ref{fig:crossval} shows the three different test error RMSE, 0-1 loss and logloss. We used different numbers of seed to have a better prediction for our test error.
\begin{figure}
\centering
\subfigure[0-1 loss]{\includegraphics[width=1\textwidth]{images/penLogRegCrossVall01Loss.eps}}
\subfigure[rmse]{\includegraphics[width=1\textwidth]{images/penLogRegrmse.eps}}
\subfigure[log loss]{\includegraphics[width=1\textwidth]{images/penLogRegLogloss.eps}}
\caption{Cross-validation : penalized logistic regression with different lambda values}
\label{fig:crossval}
\end{figure} 
\subsection{Feature transformations}
